Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-05 doc/main_jfm.tex
adding some texts

\begin{equation}
\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
  }
    \label{figure1}
\end{figure}

@@

To study the deformation of the bilayer structure under a shear flow using the proposed algorithm, 
we adopt the widely tested numerical simulations in both continuum and molecular dynamics models.
Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_0.eps}
\includegraphics[width=0.4\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}

@@

@@

Figure~\ref{figure3} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure3}
\end{figure}

>>>>

\begin{equation}
\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
  }
    \label{figure1}
\end{figure}

@@

To study the deformation of the closed bilayer structure under a shear flow using the proposed algorithm, 
we adopt a widely tested numerical simulation in both continuum and molecular dynamics models. The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
\end{center}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$.
  }
    \label{figure3}
\end{figure}

@@

Figure~\ref{figure4} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

\begin{figure}
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure4}
\end{figure}
